Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-08-29 ms.tex
started describing the chi-squared minimization search of the BOSZ models.

The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
For each parameter, we change the models by about 2 steps in the BOSZ grid.
For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
The errors are estimated from the standard deviation of the spectra over the night.

@@

>>>>

The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
For each parameter, we change the models by about 2 steps in the BOSZ grid.
For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
The errors are estimated from the standard deviation of the spectra over the night.
For now, we ignore the smoothing of the data that creates non-zero off-diagonal terms in the covariance matrix.

@@

\subsubsection{$\chi^2$ Minimization}
We downloaded a grid of BOSZ models with temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
As discussed above, we use an approximate $\chi^2$ statistic over the wavelength range covering the Mg triplet (5160 $\AA$ to 5190 $\AA$).
